\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Software Engineer II (Level 61)}
    {Microsoft - Microsoft Teams}
    {Redmond, Washington}
    {Mar 2018 -- Now}
    {
      \begin{cvitems}
        \item {Designed and implemented back-end changes in Chat Service to accommodate channel moderation and reply permission enforcement workflows -- included work related to restricting user capabilities and optimizing data fetches for the core logic.}
        \item {Designed and implemented back-end business logic and schema changes for new announcement post types, priority notifications, and pinned messages -- included work involved creating additional data properties for webclient consumption and generation of new APIs to fetch metadata on users/teams/channels/messages.}
        \item {Worked on building front-end webclient UI for Cortana Smart Replies in Teams as part of the Intelligent Solutions directive.}
        \item {Built First Message and Suggested Contacts feature in Teams to assist new customers with onboarding.}
        \item {Implemented front-end changes and coordinate with service teams to enable IT Admin Policy Control for Teams feature such as Translation and Mailhooks.}
        \item {Shipped above features to 15M+ core users as well as 3 network isolated government platforms, and assisted with monitoring/maintenance of feature health as on-call engineer.}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern}
    {Facebook - Zstandard - Infrastructure Team}
    {Menlo Park, California}
    {May 2017 -- Aug. 2017}
    {
      \begin{cvitems}
        \item {Main Project -- Developed a multi-threaded adaptive-compression tool that measures pipeline throughput and optimizes compression ratio/time tradeoff for Zstandard (hosted on GitHub).}
        \item {Deployed tool for use in server backups and measured 7-12\% storage performance improvement in network use-case.}
        \item {Side tasks -- Contributed the \texttt{--list} command to the Zstandard CLI, added dictionary support to Zstandard test generation script.}
      \end{cvitems}
    }
  \cventry
    {Software Developer Intern in Test}
    {Redfin}
    {Seattle, Washington}
    {May 2016 -- Aug. 2016}
    {
      \begin{cvitems}
        \item {Constructed a new webpage to assist with run-time feature checks, feature control, testing automation, and data tracking for experiments. Implemented improvements including additional filter/sort settings, a new search bar, and environment info display.}
        \item {Full-Stack project involving React JavaScript front-end and Java back-end.}
      \end{cvitems}
    }
  \cventry
    {Computer Science Teaching Assistant}
    {Duke University CS Department}
    {Durham, North Carolina}
    {Jan. 2015 -- May 2017}
    {
      \begin{cvitems}
        \item {CS201: Data Structures and Algorithms TA (Jan. 2015 -- May 2016), organized and led lecture-based recitations, graded student assignments and provided feedback, held regular office hours to assist students with coursework.}
        \item {CS308: Software Design and Implementation TA, responsible for grading student assignments on code quality and extensibility.}
        \item {CS330: Design and Analysis of Algorithms TA, responsible for grading student assignments and hosting office hours lectures to assist with course materials.}
      \end{cvitems}
    }
\end{cventries}
